---
title: "bookings"
author: "Tram"
date: "2024-01-10"
output: html_document
---

## Setting up my environment

Notes: Setting up my R environment by loading the following packages

```{r loading packages, message=FALSE, warning=FALSE}
library("tidyverse")
library("skimr")
library("janitor")
library("dplyr")
library("ggplot2")
```

## Import data

```{r warning=FALSE}
setwd("D:/Google DA/Portfolio Building/090123_Practices/Bookings")
hotel_bookings <- read.csv("hotel_bookings.csv")
```

## Transactions by distribution types

```{r}
ggplot(data = hotel_bookings) +
  geom_bar(aes(x = distribution_channel, fill=distribution_channel))
```

The plot shows that TA/TO channel has the most number of bookings

## The relationship between booking lead time and guests traveling with children

```{r warning=FALSE}
ggplot(data=hotel_bookings) +
  geom_point(aes(x= children, y=lead_time), color="lightblue")+
  theme_classic()
```

This plot shows that the group of guests who typically make early bookings do not have children

## Number of bookings by hotel type and market segments

```{r faceting a plot, warning=FALSE}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = hotel)) +
  facet_wrap(~market_segment)
```

Online segment generates the largest number of bookings, and these bookings are made for city hotels

## The relationship between lead time and guests traveling with children for online bookings at city hotels

### Filtering a dataset to just city hotels that are online TA

```{r filtering a dataset to just city hotels that are online TA}
onlineta_city_hotels <- filter(hotel_bookings, 
                           (hotel=="City Hotel" & 
                             hotel_bookings$market_segment=="Online TA"))
```

### Creating the plot

```{r creating the plot, warning=FALSE}
ggplot(data = onlineta_city_hotels) +
  geom_point(aes(x = lead_time, y = children), color="lightblue")+
  theme_classic()
```

* This scatterplot shows data for online bookings for city hotels

* The plot reveals that bookings with children tend to have a shorter lead time, and bookings with 3 children have a significantly shorter lead time (\<200 days)

* So, promotions targeting families can be made closer to the valid booking dates
